Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-16 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
增加对比实验

>>>>

\subsubsection{Compared with Other Methods}

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{@{}cccccc@{}}
\toprule
Method & Tracker & Backbone & Before & After & Drop Rate \\ \midrule
CSA & SiamRPN & AlexNet & 0.851 & 0.458 & 0.46 \\
Efficient & SiamFC & AlexNet & 0.72 & 0.18 & 0.75 \\
Temeorally & SiamRPN++ & ResNet-50 & 0.91 & 0.08 & 0.91 \\
Ours & SiamFC++ & GoogLeNet & 0.861 & 0.048 & 0.94 \\ \bottomrule
\end{tabular}%
}
\end{table}

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{@{}cccc@{}}
\toprule
Method & Tracker & Backbone & Precision \\ \midrule
Efficient & SiamFC & AlexNet & 42.0 \\
Tempoarlly & SiamRPN++ & ResNet-50 & 69.2 \\
Ours & SiamFC++ & GoogLeNet & 92.8 \\
\bottomrule
\end{tabular}%
}
\end{table}
